The problem and promise of scale in multilayer animal social networks

### 2020-02-15 paper/manuscript.Rmd
landcover res results

Increasing landcover resolution resulted in a decreased proportion of forage, a
rare and patchy habitat, and corresponding low connectivity of individuals in
these habitats. Mean graph strength increased consistently in winter forest and
open habitats. Mean graph strength in winter forage varied across landcover
resolutions with an increase at 250 m and decrease at 500 m. Individuals in
summer layers had consistent weak connections. Layer relevance was stable in
winter for open and forest habitats but decreased for forage habitats (Figure
\@ref(fig:lcres)b). Layer relevance was stable for all habitat classes in summer
layers. Layer similarity was stable for forest and open, except for a sharp
decrease in layer similarity in open at 100 m and 250 m (Figure
\@ref(fig:lcres)c). Layer similarity was not possible to calculate between
summer and winter forage because, at all landcover resolutions greater than 30
m, there were no individuals connected in the network layers. Individuals still
used forage habitats but given a lower availability due to increasing landcover
resolution, at a much lower rate. Connective redundancy slightly decreased as
landcover resolution increased (Figure \@ref(fig:lcres)d). These results
indicate the importance of matching landcover resolution to scale of selection
as well as ensuring the landcover product used has a resolution fine enough to
detect landscape features and habitats relevant to study species.

>>>>

Increasing landcover resolution resulted in a decreased availability of forage, a
rare and patchy habitat, and corresponding low connectivity of individuals in
these habitats. Individuals in
summer layers had consistent weak connections (Figure
\@ref(fig:lcres)a). Mean graph strength increased consistently in winter forest and
open habitats but varied in winter forage varied across landcover
resolutions with an increase at 250 m and decrease at 500 m (Figure
\@ref(fig:lcres)a).  Layer relevance was stable for all habitat classes in summer
layers; layer relevance was significantly higher in winter and stable in open and forest habitats but decreased for forage habitats (Figure
\@ref(fig:lcres)b). <!--This pattern during the winter indicates that individuals had fewer neighbours in forage habitat habitats compared to their overall neighbourhood across habitats, likely due to the patchy nature of forage-->Layer similarity was low but stable for forest and open, except for a sharp
decrease in layer similarity in open at 100 m and 250 m (Figure
\@ref(fig:lcres)c). Layer similarity was not possible to calculate between
summer and winter forage because, at all landcover resolutions greater than 30
m, there were no individuals connected in the network layers. Individuals still
used forage habitats, but given the lower availability due to increasing landcover
resolution, at a much lower rate. Connective redundancy was moderately high but decreased slightly as
landcover resolution increased, indicating that many neighbours were the same between layers, but the proportion of neighbours in each layer slightly decreased at increasing landcover resolutions (Figure \@ref(fig:lcres)d). Overall, these results
indicate the importance of matching landcover resolution to scale of selection
as well as ensuring the landcover product used has a resolution fine enough to
detect landscape features and habitats relevant to study species, such as important patchy and rare habitats.
